A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-03 paper.tex
Add description of DM and why MAM

Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:

\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
\end{itemize}

% may be removed
The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:

\begin{enumerate}
	\item Central point of failure. 
	The broker is usually held by a single organization. If the centralized server is crashed or attacked, the services will not be available. 	
	\item Data integrity.
	As broker controls the interaction between publishers and subscribers, an unreliable or compromised broker can easily tamper data streams. 
	\item Anonymity and privacy.
	Broker matches publishers and subscribers in order to relay data streams to corresponding entities. The unreliable broker can expose the subscribers' interests and personal information of both entities.  
\end{enumerate}

>>>>

Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilaty control. 
\end{itemize}

In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapts the dynamic roles than centralized one.

\subsection{Towards Decentralized Data Marketplace}
In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly  Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Message (MAM)\cite{MAM}.

The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency.  Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities of centralized pub/sub models, for instance, central point of failure, if the centralized server is crashed or attacked, the services will not be available. Therefore, we adopted decentralized pub/sub with no organization holding brokers, and the brokers are only responsible for data transmission and agreement establishment. Furthermore, the communication between entities is built via brokers, which prevents sensitive information leaks. Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.

Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated. This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality. Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.

Another key component MAM is viewed as the data storage of data marketplace which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle ,a feeless cryptocurrency designed for IoT. MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to distributed ledgers, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. Since the data is zero-value transactions on the Tangle, the concern of losing new uploaded data due to the  disconnection does not exist, participants can retrieve the authoraized data streams anytime.

\subsection{Choice of Data Storage}
In our proposed architecture, MAM is the data storage where the data assets is reserved. However, the operations of MAM are time-consuming for IoT devices, which are evaluated in Section CITE-EVALUATION-SECTION. We assume the data assets are stored in distributed data storage systems built on top of peer-to-peer (P2P) networks maintained by multiple nodes, which avoid the central point failure and security issues of central databases. Among the existing distributed storage studied in Section CITE-RELATED-WORK, different backup mechanisms and access controls strategies are proposed, however, the keys managed by participant is hard to be as small as possible especially for data streams, which is one of the scalability requirement of data marketplace mentioned above.

\subsection{Contributions}

\subsection{Paper Organization}
